---
title: "Check WHO data"
output: pdf_document
---

For 1997:present, we calculate the raw circulation intensity as the fraction of influenza samples processed that are positive for influenza A. We use country-specific data reported in WHO Flu Net, except if there are <50 samples processed within-country, we substitute regional data for that year.

$\text{raw intensity} = \frac{n_A}{n_{processed}}$

$n_A$ and $n_{processed}$ data values are reported in the raw data on WHO flu net.

We then calculate the relative intensity of influenza A ciruclation in each year $y$ as $\frac{\text{raw intensity}_y}{\text{mean}(\text{raw intensity}_y)}$. We use the relative intensity to scale the annual probability of primary infection, so that so that the probability of imprinting in a year with higher-than average influenza A circulation is slightly higher than baseline.


**Problem**

The total number of specimens processed (n_processed) should always be greater than or equal to the number of infelunza A positive specimens in a given country and year.

However, code testing revealed that in some cases (e.g. Germany, 1997), reported $n_{processed}$ values are less than $n_A$, the number of flu-A positive specimens.

The purpose of this notebook is to check how often the n_processed column violates quality checks, and to decide how to handle exceptions.

**Testing plan**

For each country and year, check that:

$n_{processed} \geq n_A+n_B$

```{r}
library(tidyverse)
source('load_data.R')
source('data_import_funs.R')
```

```{r}
check_one_country = function(country){
  max_year=2022
  min_samples_processed_per_year = 30 ## If not enough observations available, default to regional data
  
  get_country_inputs_1997_to_present(country, max_year) %>%
    #dplyr::filter(n_processed >= min_samples_processed_per_year) %>%
    mutate(data_from = paste0('country: ', country)) %>%
    mutate(check = n_processed >= n_A+n_B) %>% ## Implement check
    select(Country, Year, n_H1N1, n_H3N2, n_A, n_B, n_processed, check) %>%
    dplyr::filter(check == FALSE) ## Retun rows that fail check
}
```

```{r message=FALSE}
## Appply the test to all countries
all_failures = lapply(show_available_countries()$country, FUN = check_one_country) %>%
  bind_rows()
```

## Overall, there are 165 failures
```{r}
all_failures
```

## We eliminate most of the failures if we require >= 30 samples processed per year
```{r message=FALSE}
all_failures %>%
  filter(n_processed > 30)
```

## We eliminate most of the failures if we require >= 50 samples processed per year
```{r message=FALSE}
all_failures %>%
  filter(n_processed > 50)
```

## Check if the problem persists at the regional level
```{r}
check_one_region = function(region){
  max_year=2022
  
get_regional_inputs_1997_to_present(region, max_year) %>%
    mutate(check = n_processed >= n_A+n_B) %>% ## Implement check
    select(WHOREGION, Year, n_H1N1, n_H3N2, n_A, n_B, n_processed, check) %>%
    dplyr::filter(check == FALSE) ## Retun rows that fail check
}
```

## There are a few years in the eastern mediterranean region that lack sufficient sample numbers and fail quality checks
```{r}
lapply(show_available_regions()$region %>% parse_region_names(), check_one_region)
```


## Overall plan to implement quality checks in intensity calculation pipeline:

1. If >50 samples processed, and passes quality check (n_processed >= (n_A + n_B)), use country-specific data
2. If >50 samples processed, and passes quality check, substitute region-specific data
3. Else, if regional and country-specific data don't meet quality standards, default to the null value of intensity = 1
