---
title: "Plotting examples"
output: html_notebook
---


## Plotting examples for the imprinting calculator

Examples for the functions in `plotting_funs.R`.

Each function inputs a data frame of imprinting probabilities, output by `get_imprinting_probabilities()`.

## Load packages and depencies
```{r}
source("plotting_funs.R")
source("data_import_funs.R")
source("calculation_funs.R")
library(tidyverse)
library(knitr)
```


## `plot_one_country_year` returns a bar plot for a single country-year
```{r}
plot_one_country_year(imprinting_df = get_imprinting_probabilities(2007, "Brazil"))
```


## if more than one country year are calculated, the function returns the first unique country year in the output data frame 
```{r fig.height=2.5, fig.width=5}
plot_one_country_year(imprinting_df = get_imprinting_probabilities(2007:2010, c("Italy", "Spain", "Indonesia", "Fiji", "New Zealand")))
```


## plot_many_country_years returns:

    * a bar plot showing imprinting probs for the first 5 countries in the data frame
    * a line plot showing changes in imprinted ages over time for the first 5 countries

```{r fig.height=9, fig.width=9}
plot_many_country_years(imprinting_df = get_imprinting_probabilities(c(2007:2010, 2022), c("Italy", "Spain", "Indonesia", "Fiji", "New Zealand", "Ecuador")))
```

## If there is only one observation year, the arrow isn't plotted. 

Should we just skip the right column in this case?
```{r fig.height=9, fig.width=9}
plot_many_country_years(imprinting_df = get_imprinting_probabilities(2010, c("Italy", "Spain", "Indonesia", "Fiji", "New Zealand", "Ecuador")))
```
